---
title: "Data Exploration"
author: "Lucy Chikwetu"
date: "9/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(tidyquant)
library(ggplot2)
library(lubridate)
library(patchwork)
library(gridExtra)
library(corrplot)
library(psych)
library(DescTools)
library(VennDiagram)
library(nVennR)
library(UpSetR)
library(naniar)
library(plyr)
```
## Reading the data 
```{r, echo=FALSE}
subFormat = read.csv("submission_format.csv", header = TRUE)
tef_data = read.csv("test_set_features.csv", header=TRUE, stringsAsFactors=TRUE)
trf_data = read.csv("training_set_features.csv", header=TRUE, stringsAsFactors=TRUE)
trl_data = read.csv("training_set_labels.csv", header=TRUE, stringsAsFactors=TRUE)
testFeatures = data.frame(tef_data)
trainingFeatures = data.frame(trf_data)
trainingLabels = data.frame(trl_data)
```
### Number of Rows
```{r}
nrow(subFormat)
nrow(testFeatures)
nrow(trainingFeatures)
nrow(trainingLabels)
```
### Number of Columns 
```{r}
ncol(subFormat)
ncol(testFeatures)
ncol(trainingFeatures)
ncol(trainingLabels)
```


### Head Viewing 
* <span style="color:blue">Submission Format</span>
```{r}
head(subFormat)
```
* <span style="color:blue">Test Set Features</span>
```{r}
head(testFeatures)
```
* <span style="color:blue">Training Set Features</span>
```{r}
head(trainingFeatures)
```
* <span style="color:blue">Submission Format</span>
```{r}
head(trainingLabels)
```
### Merging training data 
```{r}
trainingDF = trainingFeatures
trainingDF$h1n1_vaccine = trainingLabels$h1n1_vaccine
trainingDF$seasonal_vaccine = trainingLabels$seasonal_vaccine
ncol(trainingDF)
```
### Checking Unique Values for Factors
* <span style="color:blue">Age Group</span>
```{r}
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "55 - 64 Years"] = "55-64"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "35 - 44 Years"] = "35-44"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "18 - 34 Years"] = "18-34"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "65+ Years"] = "65+"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "45 - 54 Years"] = "45-54"
unique(trainingFeatures["age_group"])
```
* <span style="color:blue">Education</span>
```{r}
unique(trainingFeatures["education"])
levels(trainingDF$education)[levels(trainingDF$education) == "College Graduate"] = "Grad"
levels(trainingDF$education)[levels(trainingDF$education) == "Some College"] = "College"
levels(trainingDF$education)[levels(trainingDF$education) == "< 12 Years"] = "<12 Yrs"
levels(trainingDF$education)[levels(trainingDF$education) == "12 Years"] = "12 Yrs"
```
* <span style="color:blue">Race</span>
```{r}
unique(trainingFeatures["race"])
levels(trainingDF$race)[levels(trainingDF$race) == "Other or Multiple"] = "Other"
```
* <span style="color:blue">Sex</span>
```{r}
unique(trainingFeatures["sex"])
```
* <span style="color:blue">Income Poverty</span>
```{r}
unique(trainingFeatures["income_poverty"])
levels(trainingDF$income_poverty)[levels(trainingDF$income_poverty) == "<= $75,000, Above Poverty"] = "<=75K"
levels(trainingDF$income_poverty)[levels(trainingDF$income_poverty) == "> $75,000"] = ">75K"
```
* <span style="color:blue">Marital Status</span>
```{r}
unique(trainingFeatures["marital_status"])
```
* <span style="color:blue">Rent or Own</span>
```{r}
unique(trainingFeatures["rent_or_own"])
```
* <span style="color:blue">Employment Status</span>
```{r}
unique(trainingFeatures["employment_status"])
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Not in Labor Force"] = "~Labor"
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Employed"] = "Emp"
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Unemployed"] = "unEmp"
```
* <span style="color:blue">HHS Geographical Region</span>
```{r}
unique(trainingFeatures["hhs_geo_region"])
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "oxchjgsf"] = "A"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "bhuqouqj"] = "B"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "qufhixun"] = "C"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "lrircsnp"] = "D"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "atmpeygn"] = "E"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "lzgpxyit"] = "F"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "fpwskwrf"] = "G"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "mlyzmhmf"] = "H"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "dqpwygqj"] = "I"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "kbazzjca"] = "J"
```
* <span style="color:blue">Census MSA</span>
```{r}
unique(trainingFeatures["census_msa"])
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "Non-MSA"] = "Non"
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "MSA, Principle City"] = "Principle"
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "MSA, Not Principle  City"] = "Not Principle"
```

* <span style="color:blue">Employment Industry</span>
```{r}
unique(trainingDF["employment_industry"])
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "pxcmvdjn"] = "a"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "rucpziij"] = "b"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "wxleyezf"] = "c"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "saaquncn"] = "d"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "xicduogh"] = "e"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "ldnlellj"] = "f"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "wlfvacwt"] = "g"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "nduyfdeo"] = "h"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "fcxhlnwr"] = "i"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "vjjrobsf"] = "j"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "arjwrbjb"] = "k"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "atmlpfrs"] = "l"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "msuufmds"] = "m"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "xqicxuve"] = "n"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "phxvnwax"] = "o"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "dotnnunm"] = "p"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "mfikgejo"] = "q"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "cfqqtusy"] = "r"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "mcubkhph"] = "s"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "qnlwzans"] = "t"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "haxffmxo"] = "u"
```

* <span style="color:blue">Employment Occupation</span>
```{r}
unique(trainingFeatures["employment_occupation"])
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xgwztkwe"] = "a"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xtkaffoo"] = "b"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "emcorrxb"] = "c"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "vlluhbov"] = "d"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xqwwgdyp"] = "e"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "ccgxvspp"] = "f"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "qxajmpny"] = "g"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "kldqjyjy"] = "h"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "mxkfnird"] = "i"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "hfxkjkmi"] = "j"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "bxpfxfdn"] = "k"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "ukymxvdu"] = "l"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "cmhcxjea"] = "m"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "haliazsg"] = "n"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "dlvbwzss"] = "o"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xzmlyyjv"] = "p"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "oijqvulv"] = "q"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "rcertsgn"] = "r"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "tfqavkke"] = "s"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "hodpvpew"] = "t"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "uqqtjvyb"] = "u"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "pvmttkik"] = "v"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "dcjcmpih"] = "w"
```
* <span style="color:blue">Household Children</span>
```{r}
unique(trainingFeatures["household_children"])
```
* <span style="color:blue">Household Adults</span>
```{r}
unique(trainingFeatures["household_adults"])
```
```{r}
unique(trainingDF["h1n1_vaccine"])
```


### Data Transformation
```{r}
trainingDF <- transform(trainingDF, respondent_id = as.factor(respondent_id),
                        h1n1_concern = as.integer(h1n1_concern),
                        h1n1_knowledge = as.integer(h1n1_knowledge),
                        behavioral_antiviral_meds = as.logical(behavioral_antiviral_meds),
                        behavioral_avoidance = as.logical(behavioral_avoidance),
                        behavioral_face_mask = as.logical(behavioral_face_mask),
                        behavioral_wash_hands = as.logical(behavioral_wash_hands),
                        behavioral_large_gatherings = as.logical(behavioral_large_gatherings),
                        behavioral_outside_home = as.logical(behavioral_outside_home),
                        behavioral_touch_face = as.logical(behavioral_touch_face),
                        doctor_recc_h1n1 = as.logical(doctor_recc_h1n1),
                        doctor_recc_seasonal = as.logical(doctor_recc_seasonal),
                        chronic_med_condition = as.logical(chronic_med_condition),
                        child_under_6_months = as.logical(child_under_6_months),
                        health_worker = as.logical(health_worker),
                        health_insurance = as.logical(health_insurance),
                        opinion_h1n1_vacc_effective = as.integer(opinion_h1n1_vacc_effective),
                        opinion_h1n1_risk = as.integer(opinion_h1n1_risk),
                        opinion_h1n1_sick_from_vacc = as.integer(opinion_h1n1_sick_from_vacc),
                        opinion_seas_vacc_effective = as.integer(opinion_seas_vacc_effective),
                        opinion_seas_risk = as.integer(opinion_seas_risk),
                        opinion_seas_sick_from_vacc = as.integer(opinion_seas_sick_from_vacc),
                        age_group = as.factor(age_group),
                        education = as.factor(education),
                        race = as.factor(race),
                        sex = as.factor(sex),
                        income_poverty = as.factor(income_poverty),
                        marital_status = as.factor(marital_status),
                        rent_or_own = as.factor(rent_or_own),
                        employment_status = as.factor(employment_status),
                        hhs_geo_region = as.factor(hhs_geo_region),
                        census_msa = as.factor(census_msa),
                        household_adults = as.integer(household_adults),
                        household_children = as.integer(household_children),
                        employment_industry = as.factor(employment_industry),
                        employment_occupation = as.factor(employment_occupation))
```


### Summary : Training Features
```{r}
```
```{r}
nrow(trainingDF)
ncol(trainingDF)
colnames(trainingDF)
names(which(sapply(trainingDF, anyNA)))
```

```{r}
empty <- filter(trainingDF, trainingDF$opinion_seas_vacc_effective == "")
print(colnames(trainingDF[1]))
total <- sum(is.na(trainingDF$opinion_h1n1_risk))
total2 <- total + ncol(empty)
print(ncol(empty))
print(total)
```
```{r}
total1 <- which(is.na(trainingDF$opinion_h1n1_risk))
print(sum(is.na(trainingDF$opinion_h1n1_risk)))
#print(total1)
print("\n")
total2 <- which(is.na(trainingDF$opinion_h1n1_vacc_effective))
print(sum(is.na(trainingDF$opinion_h1n1_vacc_effective)))
#print(total2)
print("\n")
total3 <- which(is.na(trainingDF$opinion_h1n1_sick_from_vacc))
print("\n")
total4 <- which(is.na(trainingDF$opinion_seas_vacc_effective))
#print(total4)
print("\n")
total5 <- which(is.na(trainingDF$opinion_seas_sick_from_vacc))
#print(total5)
print("\n")
total6 <- which(is.na(trainingDF$opinion_seas_risk))
#print(total6)
```

```{r, error=TRUE}
myv <- plotVenn(list(total1,total2,total3,total4,total5,total6), outFile="venn.svg")
showSVG(nVennObj = myv, opacity = 0.1, borderWidth = 3)
```


```{r, fig.align='center'}
pmiss <- vis_miss(trainingDF, warn_large_data = FALSE) +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, angle=0), axis.title = element_text(size=8), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
   coord_flip()
pmiss
```



```{r, fig.align='center'}
opinions = data.frame(trainingDF$opinion_h1n1_risk, trainingDF$opinion_h1n1_sick_from_vacc, trainingDF$opinion_h1n1_vacc_effective, trainingDF$opinion_seas_risk, trainingDF$opinion_seas_sick_from_vacc, trainingDF$opinion_seas_vacc_effective)
names(opinions)[names(opinions) == "trainingDF.opinion_h1n1_risk" ] = "opinion_h1n1_risk"
names(opinions)[names(opinions) == "trainingDF.opinion_h1n1_sick_from_vacc"] = "opinion_h1n1_sick_from_vacc"
names(opinions)[names(opinions) == "trainingDF.opinion_h1n1_vacc_effective"] = "opinion_h1n1_vacc_effective"
names(opinions)[names(opinions) == "trainingDF.opinion_seas_risk"] = "opinion_seas_risk"
names(opinions)[names(opinions) == "trainingDF.opinion_seas_sick_from_vacc"] = "opinion_seas_sick_from_vacc"
names(opinions)[names(opinions) == "trainingDF.opinion_seas_vacc_effective"] = "opinion_seas_vacc_effective"
gg_miss_upset(opinions,nsets=6)
```
```{r, fig.align='center'}
gg_miss_upset(trainingDF, nsets=6, order.by = "freq")
```


```{r}
venn.diagram(
   x = list(total1,total2,total3,total4,total5),
   category.names = c("h1n1_risk","h1n1_v_eff","h1n1_sick_fvacc","seas_v_eff","seas_sick_fvacc"),
   filename = "opinionVenn.png",
   cat.cex = 0.75
)
```


```{r, fig.align='center', error=TRUE}
withNA <- which(sapply(trainingDF,anyNA))
missingVals <-c()
for (col in 1:50){
   #missingVals <- c(missingVals, sum(is.na(trainingDF[col])))
   empty <- filter(trainingDF, trainingDF[col] == "")
   total <- sum(is.na(trainingDF[col]) + ncol(empty))
   print(ncol(empty))
   missingVals <- c(missingVals, sum(is.na(trainingDF[col])))
}
missingnessDF <- data.frame(cols=c(names(trainingDF)),vals=missingVals)
p1 <- ggplot(missingnessDF, aes(y=cols, x=vals)) +
      geom_col(fill="#fb6097", color="white", alpha=0.75) +
     theme(plot.title = element_text(hjust = 0.5, color="#fb6097", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
     xlab("employment industry")
p1
```
### Correlation Plot

```{r, fig.align='center', error=TRUE}
corr <- mixedCor(data=trainingDF,d=c("behavioral_antiviral_meds","behavioral_avoidance","behavioral_face_mask","behavioral_wash_hands","behavioral_large_gatherings","behavioral_outside_home","behavioral_touch_face","doctor_recc_h1n1","doctor_recc_seasonal","chronic_med_condition","child_under_6_months","health_worker","health_insurance","h1n1_vaccine","seasonal_vaccine","sex_num"), p=c("h1n1_concern","h1n1_knowledge","opinion_h1n1_vacc_effective","opinion_h1n1_risk","opinion_h1n1_sick_from_vacc","opinion_seas_vacc_effective","opinion_seas_risk","opinion_seas_sick_from_vacc","household_adults","household_children"))
corrplot(corr$rho, order="hclust", method="circle", type="upper", tl.cex=0.7,number.cex=0.5)
```
### Training Feature Plots 
```{r fig.align='center'}
trainingDF <- trainingDF %>%
   mutate(seasonal_vaccine = as.factor(seasonal_vaccine))
p1 <- ggplot(trainingDF, aes(x=h1n1_concern, fill=seasonal_vaccine)) +
      geom_bar(alpha=0.85) +
      theme_classic() +
      ggtitle("Graph of H1N1 concern frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="#464646", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("H1N1 concern") +
      scale_fill_manual(values=c("#363636", "#00be95"))
p2 <- ggplot(trainingDF, aes(h1n1_knowledge)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of H1N1 knowledge frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("H1NI knowledge")
p3 <- ggplot(trainingDF, aes(behavioral_antiviral_meds)) +
      geom_bar(fill="cyan3", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral antiviral meds frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Antiviral Meds")
p4 <- ggplot(trainingDF, aes(behavioral_avoidance)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral avoidance frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Avoidance")
(p1 + p2) / (p3 + p4)
```

```{r, fig.align='center'}
p5 <- ggplot(trainingDF, aes(behavioral_face_mask)) +
      geom_bar(fill="lightslateblue", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral face mask frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="lightslateblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Face Mask")
p6 <- ggplot(trainingDF, aes(behavioral_wash_hands)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral wash hands frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Wash Hands")
p7 <- ggplot(trainingDF, aes(behavioral_large_gatherings)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral large gatherings frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Large Gatherings")
p8 <- ggplot(trainingDF, aes(behavioral_outside_home)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral outside home frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Outside Home")
(p5+p6) / (p7+p8)
```


```{r, fig.align='center'}
p9 <- ggplot(trainingDF, aes(behavioral_touch_face)) +
      geom_bar(fill="cyan3", color="white", alpha=0.5) +
      ggtitle("Graph of behavioral touch face frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Behavioral Touch Face")
p10 <- ggplot(trainingDF, aes(doctor_recc_h1n1)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of docc_recc_h1n1 frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Doctor Rec H1N1 Vacc")
p11 <- ggplot(trainingDF, aes(doctor_recc_seasonal)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of doctor_recc_seasonal frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Doctor Rec Seasonal Flue Vacc")
p12 <- ggplot(trainingDF, aes(child_under_6_months)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of children under 6 months frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Children Under 6 Months ")
 (p9+p10) / (p11+p12)
```

```{r, fig.align='center'}
p1 <- ggplot(trainingDF, aes(health_worker)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of health worker frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Health Worker")
p2 <- ggplot(trainingDF, aes(health_insurance)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of health insurance frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("H1NI knowledge")
p3 <- ggplot(trainingDF, aes(opinion_h1n1_vacc_effective)) +
      geom_bar(fill="cyan3", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_h1n1_vacc_effective frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion H1N1 Vacc Effective")
p4 <- ggplot(trainingDF, aes(opinion_h1n1_risk)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_h1n1_risk frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion H1N1 Risk")
(p1 + p2) / (p3 + p4)
```
```{r, fig.align='center'}
p5 <- ggplot(trainingDF, aes(opinion_h1n1_sick_from_vacc)) +
      geom_bar(fill="lightslateblue", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_h1n1_sick_from_vacc frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="lightslateblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion Sick from H1N1 Vaccine")
p6 <- ggplot(trainingDF, aes(opinion_seas_vacc_effective)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_seas_vacc_effective frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion Seasonal Vaccine Effective")
p7 <- ggplot(trainingDF, aes(opinion_seas_risk)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_seas_risk frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion Seasonal Risk")
p8 <- ggplot(trainingDF, aes(opinion_seas_sick_from_vacc)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of opinion_seas_sick_from_vacc frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("Opinion Sick From Seasonal Vaccine")
(p5+p6) / (p7+p8)
```

```{r, fig.align='center'}
p9 <- ggplot(trainingDF, aes(age_group)) +
      geom_bar(fill="cyan3", color="white", alpha=0.5) +
      ggtitle("Graph of age_group frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("age_group")
p10 <- ggplot(trainingDF, aes(education)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of education frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("education")
p11 <- ggplot(trainingDF, aes(race)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of race frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("race")
p12 <- ggplot(trainingDF, aes(sex)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of sex frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("sex")
 (p9+p10) / (p11+p12)
```
```{r, fig.align='center'}
p1 <- ggplot(trainingDF, aes(income_poverty)) +
      geom_bar(fill="dodgerblue", color="white", alpha=0.5) +
      ggtitle("Graph of income_poverty frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="dodgerblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("income_poverty")
p2 <- ggplot(trainingDF, aes(marital_status)) +
      geom_bar(fill="firebrick2", color="white", alpha=0.5) +
      ggtitle("Graph of marital status frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="firebrick2", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("marital status")
p3 <- ggplot(trainingDF, aes(rent_or_own)) +
      geom_bar(fill="cyan3", color="white", alpha=0.5) +
      ggtitle("Graph of rent_or_own frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="cyan3", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("rent or own")
p4 <- ggplot(trainingDF, aes(employment_status)) +
      geom_bar(fill="gold", color="white", alpha=0.5) +
      ggtitle("Graph of employment_status frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="gold", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8)) +
      xlab("employment status")
(p1 + p2) / (p3 + p4)

```
```{r, fig.align='center'}
p1 <- ggplot(trainingDF, aes(employment_industry)) +
      geom_bar(fill="lightslateblue", color="white", alpha=0.5) +
      ggtitle("Graph of employment_industry frequency") +
      theme(plot.title = element_text(hjust = 0.5, color="lightslateblue", size=10), axis.text = element_text(size=6, color ="gray"), axis.title = element_text(size=8), axis.text.x = element_text(angle = 45, hjust=1)) +
      xlab("employment industry")
p1
```


```{r, fig.align='center', fig.width=12, fig.height=6} 
trainingDF[,2:38] %>%
   gather(-seasonal_vaccine, key="feature", value="value") %>%
   ggplot(aes(x=value, fill=seasonal_vaccine)) +
   geom_bar(alpha=0.85) +
   facet_wrap(~ feature,scales="free") +
   theme_classic() +
   theme(plot.title = element_text(hjust = 0.5, color="black", size=10), axis.text = element_text(size=6, color ="black"), axis.title = element_text(size=10), legend.text = element_text(size=8), legend.title = element_text(size=8), legend.position = "top", strip.text = element_text(size=8)) +
   xlab("Fig 1. Relationship between features and seasonal flu vaccination") +
   scale_fill_manual(values=c("#f9766d", "#00be95"))
```

