---
title: "lucyFinalContributions"
author: "Lucy Chikwetu"
date: "11/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(patchwork)
library(gridExtra)
library(psych)
library(corrplot)
library(ggfortify)
library(factoextra)
library(class) #knn
library(gmodels) # CrossTable()
library(caret) # creatFolds()
library(caTools) #sample.split()
library(ROCR) # prediction(), performance()

library(psych) # pairs.panels()
library(leaps) # regsubsets()
library(glmnet) # glmnet(), cv.glmnet(), predict()
library(plyr)
library(missForest)

set.seed(123)
```

## Reading the Data
```{r, echo=FALSE}
subFormat = read.csv("submission_format.csv", header = TRUE)
tef_data = read.csv("test_set_features.csv", header=TRUE, stringsAsFactors=TRUE)
trf_data = read.csv("training_set_features.csv", header=TRUE, stringsAsFactors=TRUE)
trl_data = read.csv("training_set_labels.csv", header=TRUE, stringsAsFactors=TRUE)
testFeatures = data.frame(tef_data)
trainingFeatures = data.frame(trf_data)
trainingLabels = data.frame(trl_data)
```

### Merging training data 
```{r}
trainingDF = trainingFeatures
trainingDF$h1n1_vaccine = trainingLabels$h1n1_vaccine
trainingDF$seasonal_vaccine = trainingLabels$seasonal_vaccine
```
### Checking Unique Values for Factors
* <span style="color:blue">Age Group</span>
```{r}
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "55 - 64 Years"] = "55-64"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "35 - 44 Years"] = "35-44"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "18 - 34 Years"] = "18-34"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "65+ Years"] = "65+"
levels(trainingDF$age_group)[levels(trainingDF$age_group) == "45 - 54 Years"] = "45-54"
```

* <span style="color:blue">Education</span>
```{r}
levels(trainingDF$education)[levels(trainingDF$education) == "College Graduate"] = "Grad"
levels(trainingDF$education)[levels(trainingDF$education) == "Some College"] = "College"
levels(trainingDF$education)[levels(trainingDF$education) == "< 12 Years"] = "<12 Yrs"
levels(trainingDF$education)[levels(trainingDF$education) == "12 Years"] = "12 Yrs"
```

* <span style="color:blue">Race</span>
```{r}
levels(trainingDF$race)[levels(trainingDF$race) == "Other or Multiple"] = "Other"
```

* <span style="color:blue">Sex</span>
```{r}
unique(trainingDF["sex"])
```
* <span style="color:blue">Income Poverty</span>
```{r}
levels(trainingDF$income_poverty)[levels(trainingDF$income_poverty) == "<= $75,000, Above Poverty"] = "<=75K"
levels(trainingDF$income_poverty)[levels(trainingDF$income_poverty) == "> $75,000"] = ">75K"
```

* <span style="color:blue">Marital Status</span>
```{r}
unique(trainingDF["marital_status"])
```
* <span style="color:blue">Rent or Own</span>
```{r}
unique(trainingDF["rent_or_own"])
```
* <span style="color:blue">Employment Status</span>
```{r}
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Not in Labor Force"] = "~Labor"
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Employed"] = "Emp"
levels(trainingDF$employment_status)[levels(trainingDF$employment_status) == "Unemployed"] = "unEmp"
```

* <span style="color:blue">HHS Geographical Region</span>
```{r}
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "oxchjgsf"] = "A"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "bhuqouqj"] = "B"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "qufhixun"] = "C"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "lrircsnp"] = "D"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "atmpeygn"] = "E"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "lzgpxyit"] = "F"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "fpwskwrf"] = "G"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "mlyzmhmf"] = "H"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "dqpwygqj"] = "I"
levels(trainingDF$hhs_geo_region)[levels(trainingDF$hhs_geo_region) == "kbazzjca"] = "J"
```

* <span style="color:blue">Census MSA</span>
```{r}
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "Non-MSA"] = "Non"
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "MSA, Principle City"] = "Principle"
levels(trainingDF$census_msa)[levels(trainingDF$census_msa) == "MSA, Not Principle  City"] = "Not Principle"
```

* <span style="color:blue">Employment Industry</span>
```{r}
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "pxcmvdjn"] = "a"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "rucpziij"] = "b"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "wxleyezf"] = "c"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "saaquncn"] = "d"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "xicduogh"] = "e"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "ldnlellj"] = "f"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "wlfvacwt"] = "g"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "nduyfdeo"] = "h"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "fcxhlnwr"] = "i"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "vjjrobsf"] = "j"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "arjwrbjb"] = "k"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "atmlpfrs"] = "l"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "msuufmds"] = "m"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "xqicxuve"] = "n"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "phxvnwax"] = "o"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "dotnnunm"] = "p"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "mfikgejo"] = "q"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "cfqqtusy"] = "r"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "mcubkhph"] = "s"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "qnlwzans"] = "t"
levels(trainingDF$employment_industry)[levels(trainingDF$employment_industry) == "haxffmxo"] = "u"
```

* <span style="color:blue">Employment Occupation</span>
```{r}
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xgwztkwe"] = "a"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xtkaffoo"] = "b"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "emcorrxb"] = "c"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "vlluhbov"] = "d"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xqwwgdyp"] = "e"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "ccgxvspp"] = "f"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "qxajmpny"] = "g"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "kldqjyjy"] = "h"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "mxkfnird"] = "i" 
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "hfxkjkmi"] = "j"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "bxpfxfdn"] = "k"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "ukymxvdu"] = "l"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "cmhcxjea"] = "m"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "haliazsg"] = "n"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "dlvbwzss"] = "o"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "xzmlyyjv"] = "p"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "oijqvulv"] = "q"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "rcertsgn"] = "r"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "tfqavkke"] = "s"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "hodpvpew"] = "t"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "uqqtjvyb"] = "u"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "pvmttkik"] = "v"
levels(trainingDF$employment_occupation)[levels(trainingDF$employment_occupation) == "dcjcmpih"] = "w"
```

* <span style="color:blue">Household Children</span>
```{r}
unique(trainingFeatures["household_children"])
```
* <span style="color:blue">Household Adults</span>
```{r}
unique(trainingFeatures["household_adults"])
```
```{r}
unique(trainingDF["h1n1_vaccine"])
```
### Data Transformation
```{r}
trainingDF <- transform(trainingDF, respondent_id = as.factor(respondent_id),
                        h1n1_concern = as.integer(h1n1_concern),
                        h1n1_knowledge = as.integer(h1n1_knowledge),
                        behavioral_antiviral_meds = as.logical(behavioral_antiviral_meds),
                        behavioral_avoidance = as.logical(behavioral_avoidance),
                        behavioral_face_mask = as.logical(behavioral_face_mask),
                        behavioral_wash_hands = as.logical(behavioral_wash_hands),
                        behavioral_large_gatherings = as.logical(behavioral_large_gatherings),
                        behavioral_outside_home = as.logical(behavioral_outside_home),
                        behavioral_touch_face = as.logical(behavioral_touch_face),
                        doctor_recc_h1n1 = as.logical(doctor_recc_h1n1),
                        doctor_recc_seasonal = as.logical(doctor_recc_seasonal),
                        chronic_med_condition = as.logical(chronic_med_condition),
                        child_under_6_months = as.logical(child_under_6_months),
                        health_worker = as.logical(health_worker),
                        health_insurance = as.factor(health_insurance),
                        sex = as.factor(sex),
                        h1n1_vaccine = as.logical(h1n1_vaccine),
                        seasonal_vaccine = as.logical(seasonal_vaccine),
                        rent_or_own = as.factor(rent_or_own),
                        marital_status = as.factor(marital_status),
                        opinion_h1n1_vacc_effective = as.integer(opinion_h1n1_vacc_effective),
                        opinion_h1n1_risk = as.integer(opinion_h1n1_risk),
                        opinion_h1n1_sick_from_vacc = as.integer(opinion_h1n1_sick_from_vacc),
                        opinion_seas_vacc_effective = as.integer(opinion_seas_vacc_effective),
                        opinion_seas_risk = as.integer(opinion_seas_risk),
                        opinion_seas_sick_from_vacc = as.integer(opinion_seas_sick_from_vacc),
                        age_group = as.factor(age_group),
                        education = as.factor(education),
                        race = as.factor(race),
                        income_poverty = as.factor(income_poverty),
                        employment_status = as.factor(employment_status),
                        hhs_geo_region = as.factor(hhs_geo_region),
                        census_msa = as.factor(census_msa),
                        household_adults = as.integer(household_adults),
                        household_children = as.integer(household_children),
                        employment_industry = as.factor(employment_industry),
                        employment_occupation = as.factor(employment_occupation))
```

## Complete-case scenario 
```{r}
#-----MAKE CHANGES HERE-------!

#completeCases <- trainingDF[complete.cases(trainingDF),]
#completeCases$respondent_id <- NULL

# Nick Completecase & Unknown
#completeCases <- read.csv("nickCompleteCase.csv",header=TRUE, stringsAsFactors = TRUE)
#completeCases <- read.csv("nickUnknown.csv",header=TRUE, stringsAsFactors = TRUE)
#completeCases$X <- NULL
#completeCases$respondent_id <- NULL

# Arinze 
completeCases <- read.csv("arinzeModel.csv",header=TRUE, stringsAsFactors = TRUE)
completeCases$X <- NULL

glimpse(completeCases)

```

## Make missingness a category in health insurance
```{r}
randImp <- trainingDF
randImp$respondent_id <- NULL
levels(randImp$health_insurance)[levels(randImp$health_insurance) == "0"] = "None"
levels(randImp$health_insurance)[levels(randImp$health_insurance) == "1"] = "Present"
levels(randImp$health_insurance) = c("None","Present","Missing")
randImp[is.na(randImp$health_insurance),'health_insurance'] <- 'Missing'
#glimpse(randImp)
#summary(randImp$health_insurance)
```

## Imputation using most frequent category
```{r}
for (i in names(randImp)){
  # Get arrays of missing values
  missing00 <- which(is.na(randImp[i]) & randImp$h1n1_vaccine == FALSE & randImp$seasonal_vaccine == FALSE  )
  missing01 <- which(is.na(randImp[i]) & randImp$h1n1_vaccine == FALSE & randImp$seasonal_vaccine == TRUE  )
  missing10 <- which(is.na(randImp[i]) & randImp$h1n1_vaccine == TRUE & randImp$seasonal_vaccine == FALSE  )
  missing11 <- which(is.na(randImp[i]) & randImp$h1n1_vaccine == TRUE & randImp$seasonal_vaccine == TRUE  )

  # Get most frequent values
  freq00 <- randImp[which.max(!is.na(randImp[i]) & randImp$h1n1_vaccine == FALSE & randImp$seasonal_vaccine == FALSE), i]
  freq01 <- randImp[which.max(!is.na(randImp[i]) & randImp$h1n1_vaccine == FALSE & randImp$seasonal_vaccine == TRUE), i]
  freq10 <- randImp[which.max(!is.na(randImp[i]) & randImp$h1n1_vaccine == TRUE & randImp$seasonal_vaccine == FALSE), i]
  freq11 <- randImp[which.max(!is.na(randImp[i]) & randImp$h1n1_vaccine == TRUE & randImp$seasonal_vaccine == TRUE), i]

  # Now we replace the values 
  randImp[missing00,i] <- freq00
  randImp[missing01,i] <- freq01
  randImp[missing10,i] <- freq10
  randImp[missing11,i] <- freq11
}

write.csv(randImp,"modImputation_health_ins_as_category.csv")
```

## Model Imputation 
```{r}
set.seed(123)
modelImp <- trainingDF
modelImp$respondent_id <- NULL
levels(modelImp$health_insurance)[levels(modelImp$health_insurance) == "0"] = "None"
levels(modelImp$health_insurance)[levels(modelImp$health_insurance) == "1"] = "Present"
levels(modelImp$health_insurance) = c("None","Present","Missing")
modelImp[is.na(modelImp$health_insurance),'health_insurance'] <- 'Missing'

# Now we have to make sure all variables are categorical
modelImp <- transform(modelImp,
                        h1n1_concern = as.integer(h1n1_concern),
                        h1n1_knowledge = as.integer(h1n1_knowledge),
                        behavioral_antiviral_meds = as.factor(behavioral_antiviral_meds),
                        behavioral_avoidance = as.factor(behavioral_avoidance),
                        behavioral_face_mask = as.factor(behavioral_face_mask),
                        behavioral_wash_hands = as.factor(behavioral_wash_hands),
                        behavioral_large_gatherings = as.factor(behavioral_large_gatherings),
                        behavioral_outside_home = as.factor(behavioral_outside_home),
                        behavioral_touch_face = as.factor(behavioral_touch_face),
                        doctor_recc_h1n1 = as.factor(doctor_recc_h1n1),
                        doctor_recc_seasonal = as.factor(doctor_recc_seasonal),
                        chronic_med_condition = as.factor(chronic_med_condition),
                        child_under_6_months = as.factor(child_under_6_months),
                        health_worker = as.factor(health_worker),
                        health_insurance = as.factor(health_insurance),
                        sex = as.factor(sex),
                        h1n1_vaccine = as.factor(h1n1_vaccine),
                        seasonal_vaccine = as.factor(seasonal_vaccine),
                        rent_or_own = as.factor(rent_or_own),
                        marital_status = as.factor(marital_status),
                        opinion_h1n1_vacc_effective = as.integer(opinion_h1n1_vacc_effective),
                        opinion_h1n1_risk = as.integer(opinion_h1n1_risk),
                        opinion_h1n1_sick_from_vacc = as.integer(opinion_h1n1_sick_from_vacc),
                        opinion_seas_vacc_effective = as.integer(opinion_seas_vacc_effective),
                        opinion_seas_risk = as.integer(opinion_seas_risk),
                        opinion_seas_sick_from_vacc = as.integer(opinion_seas_sick_from_vacc),
                        age_group = as.factor(age_group),
                        education = as.factor(education),
                        race = as.factor(race),
                        income_poverty = as.factor(income_poverty),
                        employment_status = as.factor(employment_status),
                        hhs_geo_region = as.factor(hhs_geo_region),
                        census_msa = as.factor(census_msa),
                        household_adults = as.integer(household_adults),
                        household_children = as.integer(household_children),
                        employment_industry = as.factor(employment_industry),
                        employment_occupation = as.factor(employment_occupation))

#modelImp <- missForest(modelImp)
#summary(modelImp)
```

## Splitting the data to 75:25
```{r}
set.seed(123)
sample <- sample.split(completeCases$h1n1_vaccine,SplitRatio = 0.7)
cc_train_df <- subset(completeCases,sample == TRUE)
cc_test_df <- subset(completeCases, sample == FALSE)
cc_complete_hx <- model.matrix(h1n1_vaccine~., completeCases)[,-36]
cc_complete_hy <- completeCases[,36]
cc_complete_sx <- model.matrix(seasonal_vaccine~., completeCases)[,-37]
cc_complete_sy <- completeCases[,37]

rand_sample <- sample.split(randImp$h1n1_vaccine,SplitRatio = 0.7)
rand_train_df <- subset(randImp,rand_sample == TRUE)
rand_test_df <- subset(randImp, rand_sample == FALSE)
rand_complete_hx <- model.matrix(h1n1_vaccine~., completeCases)[,-36]
rand_complete_hy <- completeCases[,36]
rand_complete_sx <- model.matrix(seasonal_vaccine~., completeCases)[,-37]
rand_complete_sy <- completeCases[,37]

#glimpse(modelImp)
#modelImp <- sample.split(modelImp$h1n1_vaccine,SplitRatio = 0.75)
#model_train_df <- subset(modelImp,rand_sample == TRUE)
#model_test_df <- subset(modelImp, rand_sample == FALSE)
#model_complete_hx <- model.matrix(h1n1_vaccine~., completeCases)[,-36]
#model_complete_hy <- completeCases[,36]
#model_complete_sx <- model.matrix(seasonal_vaccine~., completeCases)[,-37]
#model_complete_sy <- completeCases[,37]
```


```{r}
set.seed(123)
# Let's split data for Lasso
cc_train_hx <- model.matrix(h1n1_vaccine~.,cc_train_df)[,-(36:37)]
cc_train_hy = cc_train_df[,36]
cc_train_sx <- model.matrix(seasonal_vaccine~.,cc_train_df)[,-(36:37)]
cc_train_sy = cc_train_df[,37]

cc_test_hx <- model.matrix(h1n1_vaccine~.,cc_test_df)[,-(36:37)]
cc_test_hy = cc_test_df[,36]
cc_test_sx <- model.matrix(seasonal_vaccine~.,cc_test_df)[,-(36:37)]
cc_test_sy = cc_test_df[,37]

rand_train_hx <- model.matrix(h1n1_vaccine~.,rand_train_df)[,-(36:37)]
rand_train_hy = rand_train_df[,36]
rand_train_sx <- model.matrix(seasonal_vaccine~.,rand_train_df)[,-(36:37)]
rand_train_sy = rand_train_df[,37]

rand_test_hx <- model.matrix(h1n1_vaccine~.,rand_test_df)[,-(36:37)]
rand_test_hy = rand_test_df[,36]
rand_test_sx <- model.matrix(seasonal_vaccine~.,rand_test_df)[,-(36:37)]
rand_test_sy = rand_test_df[,37]

#model_train_hx <- model.matrix(h1n1_vaccine~.,model_train_df)[,-(36:37)]
#model_train_hy = model_train_df[,36]
#model_train_sx <- model.matrix(seasonal_vaccine~.,model_train_df)[,-(36:37)]
#model_train_sy = model_train_df[,37]

#model_test_hx <- model.matrix(h1n1_vaccine~.,model_test_df)[,-(36:37)]
#model_test_hy = model_test_df[,36]
#model_test_sx <- model.matrix(seasonal_vaccine~.,model_test_df)[,-(36:37)]
#model_test_sy = model_test_df[,37]

lambdaArray <- 10^(seq(from=12,to=-6, length.out = 300))
```

## Lasso Modeling 
```{r}
set.seed(123)
cc_lassoModel_hx <- glmnet(cc_train_hx, cc_train_hy, alpha = 1, lambda = lambdaArray)
cc_lassoModel_sx <- glmnet(cc_train_sx, cc_train_sy, alpha = 1, lambda = lambdaArray)

rand_lassoModel_hx <- glmnet(rand_train_hx, rand_train_hy, alpha = 1, lambda = lambdaArray)
rand_lassoModel_sx <- glmnet(rand_train_sx, rand_train_sy, alpha = 1, lambda = lambdaArray)

#model_lassoModel_hx <- glmnet(model_train_hx, model_train_hy, alpha = 1, lambda = lambdaArray)
#model_lassoModel_sx <- glmnet(model_train_sx, model_train_sy, alpha = 1, lambda = lambdaArray)
```

## get minimums
```{r}
set.seed(123)
cc_hx <- cv.glmnet(cc_train_hx,cc_train_hy, alpha=1)
cc_sx <- cv.glmnet(cc_train_sx,cc_train_sy, alpha=1)

rand_hx <- cv.glmnet(rand_train_hx,rand_train_hy, alpha=1)
rand_sx <- cv.glmnet(rand_train_sx,rand_train_hy, alpha=1)

#model_hx <- cv.glmnet(cc_train_hx,cc_train_hy, alpha=1)
#model_sx <- cv.glmnet(model_train_sx,model_train_sy, alpha=1)
```

## predictions 
```{r}
set.seed(123)
sigmoid = function(x) {
   1 / (1 + exp(-x))
}

print("---------------------------------------Complete Case H1N1------------------------------------------")
cc_hx_pred <- predict(cc_lassoModel_hx, s=cc_hx$lambda.min, newx = cc_test_hx)
mean((cc_hx_pred - cc_test_hy)^2) #mean squared error (MSE)
cc_h_labels <- data.frame(cbind( actual=cc_test_df$h1n1_vaccine, pred=sigmoid(cc_hx_pred))) 
cc_h_labels <- cc_h_labels %>%
                  mutate(logicalPred = ifelse(cc_h_labels$X1 > 0.611, 1, 0)) #0.625(Lucy) #0.62(Arinze) #0.611(Nick Unknown)
cc_h_labels$actual = as.factor(cc_h_labels$actual)
cc_h_labels$logicalPred = as.factor(cc_h_labels$logicalPred)
summary(cc_h_labels)
confusionMatrix(cc_h_labels$logicalPred,cc_h_labels$actual)
print("---------------------------------------------------------------------------------------------------")

print("--------------------------------------Complete Case Seasonal Flu-----------------------------------")
cc_sx_pred <- predict(cc_lassoModel_sx, s=cc_sx$lambda.min, newx = cc_test_sx)
mean((cc_sx_pred - cc_test_sy)^2) #mean squared error (MSE)
cc_s_labels <- data.frame(cbind( actual=cc_test_df$seasonal_vaccine, pred=sigmoid(cc_sx_pred))) 
cc_s_labels <- cc_s_labels %>%
                  mutate(logicalPred = ifelse(cc_s_labels$X1 > 0.62, 1, 0)) #0.6135(Lucy) #0.62(Arinze) #0.62(Nick Unknown)
cc_s_labels$actual = as.factor(cc_s_labels$actual)
cc_s_labels$logicalPred = as.factor(cc_s_labels$logicalPred)
summary(cc_s_labels)
confusionMatrix(cc_s_labels$logicalPred,cc_s_labels$actual)
print("--------------------------------------------------------------------------------------------------")

print("----------------------------------------Mod H1N1---------------------------------------------------")
rand_hx_pred <- predict(rand_lassoModel_hx, s=rand_hx$lambda.min, newx = rand_test_hx)
mean((rand_hx_pred - rand_test_hy)^2) #mean squared error (MSE)
rand_h_labels <- data.frame(cbind( actual=rand_test_df$h1n1_vaccine, pred=sigmoid(rand_hx_pred))) 
rand_h_labels <- rand_h_labels %>%
                  mutate(logicalPred = ifelse(rand_h_labels$X1 > 0.625, 1, 0))
rand_h_labels$actual = as.factor(rand_h_labels$actual)
rand_h_labels$logicalPred = as.factor(rand_h_labels$logicalPred)
summary(rand_h_labels)
confusionMatrix(rand_h_labels$logicalPred,rand_h_labels$actual)
print("-------------------------------------------------------------------------------------------------")

print("----------------------------------------Mod Seasonal Flu-----------------------------------------")
rand_sx_pred <- predict(rand_lassoModel_sx, s=rand_sx$lambda.min, newx = rand_test_sx)
mean((rand_sx_pred - rand_test_sy)^2) #mean squared error (MSE)
rand_s_labels <- data.frame(cbind( actual=rand_test_df$seasonal_vaccine, pred=sigmoid(rand_sx_pred))) 
rand_s_labels <- rand_s_labels %>%
                  mutate(logicalPred = ifelse(rand_s_labels$X1 > 0.6125, 1, 0))
rand_s_labels$actual = as.factor(rand_s_labels$actual)
rand_s_labels$logicalPred = as.factor(rand_s_labels$logicalPred)
summary(rand_s_labels)
confusionMatrix(rand_s_labels$logicalPred,rand_s_labels$actual)
print("-------------------------------------------------------------------------------------------------")

#model_hx_pred <- predict(model_lassoModel_hx, s=model_hx$lambda.min, newx = model_test_hx)
#mean((model_hx_pred - model_test_hy)^2) #mean squared error (MSE)
#model_sx_pred <- predict(model_lassoModel_sx, s=model_sx$lambda.min, newx = model_test_sx)
#mean((model_sx_pred - model_test_sy)^2) #mean squared error (MSE)
```

# 
```{bash}

```



